---
output: pdf_document
geometry: "top = 0.75in, left = 0.5in, right = 0.5in, bottom = 0.1in"
header-includes: 
  - \usepackage{booktabs}
  - \usepackage{nopageno}
  - \usepackage{caption}
  - \captionsetup{labelformat = empty, justification = justified}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, comment = "", warning = FALSE, message = FALSE,
  fig.height = 1.8, fig.width = 2.5, fig.align = "center"
)
```


\large Table: Binomial cumulative distribution function (CDF) probabilities
\vspace{0.2in}


```{r message = FALSE}
suppressWarnings(library(ggplot2)); theme_set(theme_classic())
suppressWarnings(library(latex2exp))

x <- 0:10
y <- dbinom(x, 10, 0.2)
fillcol <- c(rep("yes", 3), rep("no", 8))

df <- data.frame(x = x, y = y, fillcol = fillcol)

ggplot(df, aes(x = x, y = y, fill = fillcol)) + 
  geom_bar(stat = "identity", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  scale_y_continuous("P(X = x)", limits = c(NA, 0.4), breaks = seq(0, 0.4, 0.1)) +
  scale_fill_manual(values = c("yes" = "black", "no" = "white"), guide = FALSE) +
  geom_segment(
    x = 5, y = 0.32, 
    xend = 2.8, yend = 0.25, 
    arrow = arrow(length = unit(0.1, "cm"), type = "closed"),
    size = 0.3
  ) +
  annotate(geom = "text",
    x = 7.6, y = 0.38,
    label = "Total shaded area:",
    size = 4, family = "serif"
  ) +
  annotate(geom = "text",
    x = 7.8, y = 0.32,
    label = TeX("P($X\\leq 2$) for", output = "character"),
    parse = TRUE, size = 4, family = "serif"
  ) +
  annotate(geom = "text",
    x = 7.8, y = 0.27,
    label = "paste(italic(n), \" = 10, \", italic(p), \" = 0.2 \")",
    parse = TRUE, size = 4, family = "serif"
  ) +
  theme(
    axis.text = element_text(size = 9, color = "black"),
    text = element_text(family = "serif"),
    title = element_text(family = "serif"),
    axis.title.x = element_text(margin = margin(t = 2)),
    axis.title.y = element_text(margin = margin(r = 2))
  )
```


$n=2$


```{r results = "asis", message = FALSE}
suppressWarnings(library(xtable))
suppressWarnings(library(magrittr))

make_binom_table <- function(trials) {

  x <- 0:trials
  p <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
  
  x_p_pairs <- expand.grid(x = x, p = p)
  
  probs <- Map(pbinom, 
    q = x_p_pairs$x,
    size = trials,
    prob = x_p_pairs$p
  )
  table_probs <- probs %>% 
    unlist() %>%
    round(input$round_digits) %>%
    matrix(nrow = length(x), byrow = FALSE)
  
  table_probs_new <- cbind.data.frame(x, table_probs)
  
  col_names <- formatC(signif(p, 2), format = "f", digits = 2)
  col_names_centered <- paste0("\\multicolumn{1}{c}{", col_names, "}")
  
  colnames(table_probs_new) <- c("xp", col_names_centered)
  
  
  if (input$drop_lead_zeros) {
    table_probs_new[, -1] <- apply(table_probs_new[, -1], 2, 
      function(.) gsub("^0.", ".", sprintf(paste0("%.", input$round_digits, "f"), .))
    )
  
    colnames(table_probs_new) <- gsub("\\{0.", "\\{.", colnames(table_probs_new))
  }
  
  
  format_col_names <- function(x) {
    x <- gsub("xp", "$\\x \\\\, \\\\backslash \\\\, \\p$", x)
    x
  }
  
  
  if (input$round_digits < 5) {
    print(
      xtable::xtable(table_probs_new, 
        digits = c(0, 0, rep(input$round_digits, length(p))),
        align = c("c|", "c|", rep("r", length(p))),
        type = "latex"
      ),
      include.rownames = FALSE,
      sanitize.colnames.function = format_col_names,
      comment = FALSE,
      booktabs = TRUE,
      table.placement = "!ht"
    )
  } else {
    print(
      xtable::xtable(table_probs_new, 
        digits = c(0, 0, rep(input$round_digits, length(p))),
        align = c("c|", "c|", rep("r", length(p))),
        type = "latex"
      ),
      include.rownames = FALSE,
      size = "\\fontsize{8}{10}\\selectfont",
      sanitize.colnames.function = format_col_names,
      comment = FALSE,
      booktabs = TRUE,
      table.placement = "!ht"
    )
  }
}

make_binom_table(2)
```


$n=3$

```{r results = "asis"}
make_binom_table(3)
```


$n=4$

```{r results = "asis"}
make_binom_table(4)
```


$n=5$

```{r results = "asis"}
make_binom_table(5)
```


\newpage

\large Table: Binomial cumulative distribution function (CDF) probabilities (continued)
\vspace{0.25in}


$n=6$

```{r results = "asis"}
make_binom_table(6)
```


$n=7$

```{r results = "asis"}
make_binom_table(7)
```


$n=8$

```{r results = "asis"}
make_binom_table(8)
```


$n=9$

```{r results = "asis"}
make_binom_table(9)
```


\newpage

\large Table: Binomial cumulative distribution function (CDF) probabilities (continued)
\vspace{0.25in}


$n=10$

```{r results = "asis"}
make_binom_table(10)
```


$n=15$

```{r results = "asis"}
make_binom_table(15)
```


\newpage

\large Table: Binomial cumulative distribution function (CDF) probabilities (continued)
\vspace{0.25in}


$n=20$

```{r results = "asis"}
make_binom_table(20)
```


\newpage

\large Table: Binomial cumulative distribution function (CDF) probabilities (continued)
\vspace{0.25in}


$n=25$

```{r results = "asis"}
make_binom_table(25)
```



