---
output: pdf_document
geometry: "top = 0.75in, left = 0.5in, right = 0.5in, bottom = 0.1in"
header-includes: 
  - \usepackage{booktabs}
  - \usepackage{nopageno}
  - \usepackage{caption}
  - \captionsetup{labelformat = empty, justification = justified}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, comment = "", warning = FALSE, message = FALSE,
  fig.height = 1.8, fig.width = 2.5, fig.align = "center"
)
```


\large Table: Poisson probability mass function (PMF) probabilities
\vspace{0.2in}


```{r message = FALSE}
suppressWarnings(library(ggplot2)); theme_set(theme_classic())

x <- 0:10
lam <- 2
y <- dpois(x, lam)
fillcol <- c(rep("no", 2), "yes", rep("no", 8))

df <- data.frame(x = x, y = y, fillcol = fillcol)

ggplot(df, aes(x = x, y = y, fill = fillcol)) + 
  geom_bar(stat = "identity", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  scale_y_continuous("P(X = x)", limits = c(NA, 0.35), breaks = seq(0, 0.3, 0.1)) +
  scale_fill_manual(values = c("yes" = "black", "no" = "white"), guide = FALSE) +
  geom_segment(
    x = 5.2, y = 0.22, 
    xend = 2.8, yend = 0.265, 
    arrow = arrow(length = unit(0.1, "cm"), type = "closed"),
    size = 0.3
  ) +
  annotate(geom = "text",
    x = 7.8, y = 0.22,
    label = "P(X = 2) for",
    size = 4, family = "serif"
  ) +
  annotate(geom = "text",
    x = 7.8, y = 0.17,
    label = "paste(lambda, \" = 2\")",
    parse = TRUE, size = 4, family = "serif"
  ) +
  theme(
    axis.text = element_text(size = 9, color = "black"),
    text = element_text(family = "serif"),
    title = element_text(family = "serif"),
    axis.title.x = element_text(margin = margin(t = 2)),
    axis.title.y = element_text(margin = margin(r = 2))
  )
```


\vspace{0.1in}


```{r results = "asis", message = FALSE}
suppressWarnings(library(xtable))
suppressWarnings(library(magrittr))

make_pois_table <- function(x_max, lambda) {

  x <- 0:x_max
  
  x_lambda_pairs <- expand.grid(x = x, lambda = lambda)
  
  probs <- Map(dpois, 
    x = x_lambda_pairs$x,
    lambda = x_lambda_pairs$lambda
  )
  table_probs <- probs %>% 
    unlist() %>%
    round(input$round_digits) %>%
    matrix(nrow = length(x), byrow = FALSE)
  
  table_probs_new <- cbind.data.frame(x, table_probs)
  
  col_names <- formatC(signif(lambda, 3), format = "f", digits = 1)
  col_names_centered <- paste0("\\multicolumn{1}{c}{", col_names, "}")
  
  colnames(table_probs_new) <- c("xlam", col_names_centered)
  
  
  if (input$drop_lead_zeros) {
    table_probs_new[, -1] <- apply(table_probs_new[, -1], 2, 
      function(.) gsub("^0.", ".", sprintf(paste0("%.", input$round_digits, "f"), .))
    )
  
    colnames(table_probs_new) <- gsub("\\{0.", "\\{.", colnames(table_probs_new))
  }
  
  
  format_col_names <- function(x) {
    x <- gsub("xlam", "$\\x \\\\, \\\\backslash \\\\, \\\\lambda$", x)
    x
  }
  
  
  print(
    xtable::xtable(table_probs_new, 
      digits = c(0, 0, rep(input$round_digits, length(lambda))),
      align = c("c|", "c|", rep("r", length(lambda))),
      type = "latex"
    ),
    include.rownames = FALSE,
    sanitize.colnames.function = format_col_names,
    comment = FALSE,
    booktabs = TRUE,
    table.placement = "!ht"
  )
}

make_pois_table(16, seq(0.5, 5, 0.5))
```


\newpage


\large Table: Poisson probability mass function (PMF) probabilities (continued)
\vspace{0.25in}


```{r results = "asis"}
make_pois_table(25, seq(5.5, 10, 0.5))
```


\newpage


\large Table: Poisson probability mass function (PMF) probabilities (continued)
\vspace{0.25in}


```{r results = "asis"}
make_pois_table(33, seq(10.5, 15, 0.5))
```


\newpage


\large Table: Poisson probability mass function (PMF) probabilities (continued)
\vspace{0.25in}


```{r results = "asis"}
make_pois_table(40, seq(15.5, 20, 0.5))
```



